---
title: "R Notebook for Color Transformation RGB2Lab"
output: html_notebook
---

### **Objective**

This is the code to transform all images in a folder (must be 24 bit RGB images) into a single CSV file containing the color information of each pixel in Lab color space.

The output file is organized as follows:

Columns:

1.  Filename

2.  L

3.  a

4.  b

Rows:

Each row corresponds to the respective information of a single pixel in the images.

### **Limitations**

It only works for 24bit images.

### Code

```{r}
## Load up packages I'm going to use first.
library(imager) 
library(data.table)

#set the working directory from which the files will be read from
my_path="C:/Users/usuario/Desktop/Work/Research/Papers/0_RipenessFreshnessAnaMaria/Frescura_frutas/Lulo/24bitBMP/P3"
setwd(my_path)

#create a list of the files from your target directory
file_list <- list.files(path=my_path)

DTP = data.table( Name=character() , L=numeric() , a=numeric() , b=numeric() )

for (k in 1:length(file_list))
{
    image <- load.image(file_list[k])
    # plot(image)
    image.lab <- RGBtoLab(image) #solo funciona para imagenes de 24 bit
    l <- data.table(image.lab[,,1,1])
    
    for(i in 1:nrow(l))
    {
      for(j in 1:ncol(l))
      {
          DT2 = data.table(Name=file_list[k],L=image.lab[i,j,,1],a=image.lab[i,j,,2],b=image.lab[i,j,,3])
          DTP <- rbindlist(list(DTP, DT2)) #adding row info to DT, #for each iteration, bind the new data to the building dataset
      }
    }

}

write.csv2(DTP, file = "result.csv",row.names = FALSE)

```

```{r}

```

\`\`\`
